Model Finding for Recursive Functions in SMT\thanks{ This research is partially supported by the Inria technological development action ``Contre-exemples utilisables par Isabelle et Coq'' (CUIC). }

### 2015-11-24 smt2015/body.tex
removed, tuned

\begin{longv}
Most of the above tools cannot cope with algebraic datatypes or other infinite
types. \end{longv}%
Kuncak and Jackson \cite{kuncak-jackson-2005} presented an idiom for
encoding datatypes and recursive functions in Alloy, by approximating datatypes
by finite subterm-closed substructures. The approach finds sound (fragments
of) models for formulas in the \relax{existential--bounded-universal} fragment
\begin{longv}(i.e., formulas whose prenex normal forms contain no unbounded universal
quantifiers ranging over datatypes)\end{longv}. This idiom was further developed by Dunets
et al.\ \cite{dunets-et-al-2010}, who presented a translation scheme
for primitive recursion. Their definedness guards play a similar role to the
existential constraints generated by our translation $\conv$.

>>>>

\begin{longv}
Most of the above tools cannot cope with algebraic datatypes or other infinite
types. \end{longv}%
Kuncak and Jackson \cite{kuncak-jackson-2005} presented an idiom for
encoding datatypes and recursive functions in Alloy, by approximating datatypes
by finite subterm-closed substructures. The approach finds sound (fragments
of) models for formulas in the \relax{existential--bounded-universal} fragment%
\begin{longv} (i.e., formulas whose prenex normal forms contain no unbounded universal
quantifiers ranging over datatypes)\end{longv}. This idiom was further developed by Dunets
et al.\ \cite{dunets-et-al-2010}, who presented a translation scheme
for primitive recursion. Their definedness guards play a similar role to the
existential constraints generated by our translation $\conv$.
